---
title: "Naecker Lab HLM Brainstorm"
author: "Kelly Jamrog"
date: "4/19/2018"
output: html_document
---

###Model 1: 
Predict the choice an individual will make based off of round characteristics, 
game characteristics, and personal characteristics.  

###Response variable: B
  - 1 = option B
  - 0 = option A
  
###Model 2: 
Predict if an individual will change their choice based off of round characteristics, game characteristics, and personal characteristics. 

###Response Variable: change
  - 1 = change selected option from prior round
  - 0 = did not change selected option from prior round

###The Data:
The data has 3 levels of nesting:

  - Level 1: Round (~25 per game, total: 51,0750 )
  
      - Variables: B, Payoff, Forgone, Feedback, win_mag, win, lag
      
  - Level 2: Game  (~30 per individual, total:20,430)
  
      - Variables: Ha, pHa, La, Hb, pHb, Lb stay the same within a game
      
        - create aggregates that quantify the "success" of previous games
      
      
  - Level 3: Individual (686 individuals)
      -Variables: create aggregates that quantify characteristics of the player (gender)
      

###Potential Issues:
We do not have data on many individual level characteristics.  If we create our own aggregate variables, will we have an issue of multicollinearity (or independence issues)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(descr) # frequency tables and descriptive statistics. freq function
library(dplyr)
library(Hmisc)
library(lme4) ## linear mixed effects models
library(merTools)
library(reshape)
library(plyr)
library(effects) 
library(binhf)
##Data Management
##import the dataset
df <- read.csv("E:/Senior/RA/cpc/cpc18/data/raw-data.csv")

##Subset data
df2<- df[, c(1, 7, 21, 8:10, 13:15, 22:25, 29)]
df2 <- df2[order(df2$SubjID, df2$GameID, df2$Trial),]

#make the button they selected into a factor
df2$Button <- as.factor(df$Button)
df2$GameID <- as.factor(df2$GameID)


df2$win_mag <- df2$Payoff - df2$Forgone
df2$win <- ifelse(df2$Payoff - df2$Forgone > 0, 1, 0)

##did their decison change
##take previous choice, see if it is different from current choice
df3 <- df2 %>%
  group_by(SubjID, GameID)%>%
  mutate(lag = shift(B, 1),
         change = ifelse(B == lag, 0 ,1))
```

##Data Exploration 
Plotting the mean value of which choice an individual will make by game:

This graph shows the variation in choice made by game.  It would appear that there is a fairly large variance in what choice an individual will make between the different games. 
```{r}
##plot the mean values of your response variable 
cdata <- ddply(df3, c("GameID"), summarise,
               N    = sum(!is.na(B)),
               mean = mean(B, na.rm=TRUE),
               sd   = sd(B, na.rm=TRUE),
               se   = sd / sqrt(N))

# reorder observations by mean school appreciation 
cdata$GameID <- factor(cdata$GameID, levels = cdata$GameID[order(cdata$mean)])

plot <- ggplot(cdata, aes(x= GameID, y = mean))
plot + geom_point() + geom_errorbar(aes(ymin=mean-se, ymax=mean+se), width=.4) + xlab("GameID") + ylab("B")

```

##hlm1: Unconditional Random Effects Model
No predictors in this model

Goal: estimate the amt of variation between group (level 2 variance)
relative to within group (level 1 variance) 

I think I did something wrong here because the output is not what I was expecting.

```{R}
hlm1 <- glmer(change ~ 1 + (1|GameID), df3, family = binomial)
summary(hlm1)


hlm2 <- glmer(change ~ 1 + Trial + (1|GameID), df3, family = binomial)
summary(hlm2)

anova(hlm1, hlm2)


hlm3 <- glmer(change ~ 1 + Trial +  (1 + Trial|GameID), df3, family = binomial)
summary(hlm3)

anova(hlm2, hlm3)


hlm4 <- glmer(change ~ 1 + Trial +  (1 + Trial|GameID), df3, family = binomial)
summary(hlm4)

anova(hlm3, hlm4)




#hlm1boot <- confint(hlm1, method="boot", oldNames = F)
#print(hlm1boot)
```
Ideas for other types of analysis:
  Using maybe a PCA approach to pull out predictive factors to throw into a more traditional statistical approach.


